Instructions for ACL 2020 Proceedings

### 2019-12-02 reports/ACL2020 Paper/acl2020-paper.tex
add some to the data section

\section{Data}
% - DA distribution              % Vlad
% - Laughter frequencies per DA  % Vlad
% - AMI, SWBD + comparison table % Bill
% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill

>>>>

\section{Data}
We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA).

% - DA distribution              % Vlad
% - Laughter frequencies per DA  % Vlad

% - AMI, SWBD + comparison table % Bill
\begin{table}[]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Switchboard}       & \textbf{AMI Corpus}                     \\ \midrule
Dyadic                     & Multi-party                             \\
Casual conversation        & Mock business meeting                   \\
Telephone                  & In-person \& video                      \\ \midrule
English                    & English                                 \\ 
Native speakers            & Native \& non-native speakers           \\ 
early '90s                 & 2000s                                   \\ \midrule
2200 conversations         & 171 meetings                            \\
  \hspace{1em} 1155 in SWDA               & \hspace{1em} 139 in AMI-DA                           \\
400 utterances             & 118k utterances                         \\
3M tokens                  & 1.2M tokens                             \\ \bottomrule
\end{tabular}
  \caption{Comparison between Switchboard and the AMI Meeting Corpus}
  \label{table:corpora}
\end{table}

% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill
